---
title: "Exercise 1"
author: "202341436"
date: "November 2 2023"
output: html_document
---

```{r setup, include=FALSE} 
# this chunk contains code that sets global options for the entire .Rmd. 
# we use include=FALSE to suppress it from the top of the document, but it will still appear in the appendix. 

knitr::opts_chunk$set(echo = FALSE) # actually set the global chunk options. 
# we set echo=FALSE to suppress code such that it by default does not appear throughout the document. 
# note: this is different from .Rmd default
```

```{r ex1}
#Define a function that can multiply the data
multiply_data <- function(data, multiplier = 2) {
  result <- data * multiplier
  return(result)
}
```

### Description:
The multiply_data function is designed to multiply data by a specified multiplier. You can easily scale your data by applying a multiplication factor.

### Parameters:
data: This parameter is mandatory. It should be the data vector or data frame that you want to change in scale.
multiplier: An optional parameter that specifies the multiplication factor. The default value is 2.

### Usage:
This will show you how to use the multiply_data function:
1. Prepare the data that you want to modify with a optional multiplier.
2. Call the multiply_data function: Input your data and the multiplier. If you don't input the multiplier, it will be a default value 2.

For example: Multiply the my_data vector by 5

```{r echo=TRUE, eval=TRUE} 
# Prepare a data vector
example_data <- c(1, 3, 5, 7, 9)

# Multiply the data by 5
example_result <- multiply_data(example_data, 5)

# Show the result
example_result

#Or print the result
print(example_result)
```

If you don't input the multiplier
```{r echo=TRUE, eval=TRUE} 
# Prepare a data vector
example_data <- c(1, 2, 3, 4, 5)

# Multiply the data by default
example_result1 <- multiply_data(example_data)

# Show the result
example_result1

#Or print the result
print(example_result1)
```

## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 
# this chunk generates the complete code appendix. 
# eval=FALSE tells R not to run (``evaluate'') the code here (it was already run before).
```
